Conservation decision-making under long transients

### 2019-08-13 slides/solarized.Rmd
update slides, compress images

background-image: url(img/royalsociety/penguin-swim.jpg)
background-position: center
background-size: 120%
class: center, top

@@

## UC Berkeley
---
layout: true
background-color: #fdf6e3
class: top

@@

![](img/royalsociety/penguin-swim.jpg)

>>>>

background-color: #fdf6e3
background-image: url(img/royalsociety/penguin-swim.jpg)
background-position: center
background-size: 120%
class: center, top

@@

### *UC Berkeley*

---
layout: true
background-color: #fdf6e3
class: top

---
class: center, top

@@

<img src="img/royalsociety/penguin-swim.jpg" width="500px">
